### 2018-02-01 submission/manuscript.tex
remove what the taq component

\section{What the Taq? The Influence of High Fidelity DNA Polymerase on
16S rRNA Gene
Sequencing}\label{what-the-taq-the-influence-of-high-fidelity-dna-polymerase-on-16s-rrna-gene-sequencing}

>>>>

\section{The Influence of High Fidelity DNA Polymerase on 16S rRNA Gene
Sequencing}\label{the-influence-of-high-fidelity-dna-polymerase-on-16s-rrna-gene-sequencing}
